### 2022-06-12 paper.tex
added e-mail addresses

\usepackage[a4paper,hmargin=1.5cm,vmargin=2.5cm,]{geometry}
\setlength{\columnsep}{0.7cm}
\usepackage{microtype} % nice typesetting
\usepackage{amsmath}
\usepackage{graphicx}

@@

@@

\twocolumn[{%
\centering
\textbf{\Large Analysing single-cell bisulfite sequencing data with \texttt{scbs}}

Lukas P.~M. Kremer\textsuperscript{1,2}, Leonie Küchenhoff\textsuperscript{1,2}, Santiago Cerrizuela\textsuperscript{2}, ..., Ana Martin-Villalba\textsuperscript{2}, Simon Anders\textsuperscript{1}\\
{\footnotesize \textsuperscript{1} BioQuant, University of Heidelberg, Germany}\\
{\footnotesize \textsuperscript{2} Molecular Neurobiology, German Cancer Research Center (DKFZ), Heidelberg, Germany}
\vspace{1.5ex}

March 2022
\vspace{6ex}
}]

\section{Abstract}

@@

The first data set is a single-cell multi-omic data set generated by \citet{argelaguet2019gastru}. In their work, the authors obtained single-cell methylomes of mouse embryo cells across different stages of development (E4.5~–~E7.5), as well as single-cell transcriptomes from the same cells. They calculated the correlation between gene expression and promoter methylation to elucidate the implications of the epigenome on gene expression in development. The authors identified several genes where promoter methylation predicts gene expression, but obtained low correlations for the vast majority of genes.

We reasoned that VMRs obtained with the previously described sliding window approach might be a better predictor of gene expression. 
In Figure \ref{figure:correlation}A, we compare correlations of gene expression and promoter methylation to correlations of gene expression and methylation of the closest VMR identified with \texttt{scbs scan}.
This analysis revealed a number of genes whose expression does not correlate with promoter methylation, but correlates with VMR methylation.
This effect is also observed when using our proposed measure of methylation, the shrunken mean of residuals (Figure \ref{figure:correlation}B).

>>>>

\usepackage[a4paper,hmargin=1.5cm,vmargin=2.5cm,]{geometry}
\setlength{\columnsep}{0.7cm}
%\usepackage{microtype} % nice typesetting  % doesn't work for me :-( -S
\usepackage{amsmath}
\usepackage{graphicx}

@@

\newcommand\blfootnote[1]{%
	\begingroup
	\renewcommand\thefootnote{}\footnote{#1}%
	\addtocounter{footnote}{-1}%
	\endgroup
}

@@

\twocolumn[{%
\centering
\textbf{\Large Analysing single-cell bisulfite sequencing data with \texttt{scbs}}\\[1.5ex]

Lukas P.~M. Kremer\textsuperscript{1,2,*}, Leonie Küchenhoff\textsuperscript{1,2}, Santiago Cerrizuela\textsuperscript{2}, ..., Ana Martin-Villalba\textsuperscript{2}, Simon Anders\textsuperscript{1,*}\\[1ex]
{\footnotesize \textsuperscript{1} BioQuant Centre, University of Heidelberg, Heidelberg, Germany\\[-.5ex]
\textsuperscript{2} Molecular Neurobiology Dept., German Cancer Research Center (DKFZ), Heidelberg, Germany}
\vspace{1.5ex}

March 2022
\vspace{6ex}
}]
\blfootnote{\hspace{-.5cm}\raggedright\textsuperscript{*} e-mail:  \texttt{l.kremer@dkfz-heidelberg.de} and\\ \hspace{1cm}\texttt{simon.anders@bioquant.uni-heidelberg.de}}
\section{Abstract}

@@

The first data set is a single-cell multi-omics data set generated by \citet{argelaguet2019gastru}. In their work, the authors obtained single-cell methylomes of mouse embryo cells across different stages of development (E4.5--E7.5) as well as single-cell transcriptomes from the same cells. They calculated the correlation between gene expression and promoter methylation to elucidate the implications of the epigenome on gene expression in development. The authors identified several genes where promoter methylation predicts gene expression, but obtained low correlations for the vast majority of genes. We reasoned that VMRs obtained with the previously described sliding window approach might be a better predictor of gene expression.

In Figure \ref{figure:correlation}A, we compare correlations of gene expression and promoter methylation to correlations of gene expression and methylation of the closest VMR identified with \texttt{scbs scan}.
This analysis revealed a number of genes whose expression does not correlate with promoter methylation, but correlates with VMR methylation.
This effect is also observed when using our proposed measure of methylation, the shrunken mean of residuals (Figure \ref{figure:correlation}B).
